Growth Resilience

### 2017-06-21 analysis/analysis_resilience_bai.Rmd
update references analysis

---
title: "Growth Resilience"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 June"
output:  
  md_document:
    variant: markdown_github
bibliography: references.bib 
csl: ecology.csl
---

>>>>

---
title: "Growth Resilience"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 June"
output:  
  md_document:
    variant: markdown_github
bibliography: ../references.bib 
csl: ../ecology.csl
---
